---
title: "Bushfire vs Covid v1"
author: "Francesco Bailo"
date: "2020-05-04"
output:
  github_document:
    toc: true
    toc_depth: 2
---

```{r, warning=F, message=F}
library(ggplot2)
library(dplyr)
library(knitr)
```

Media Cloud data (mediacloud.org) collected on 4 May 2020.

# Bushfire

```{r}
raw_bush.df <- 
  read.csv("bushfire-all-story-urls-20200504060053.csv",
           stringsAsFactors = F)
raw_bush.df$posix <- 
  as.POSIXct(raw_bush.df$publish_date, tz = "CET")
```

* Records: `r nrow(raw_bush.df)`
* Search term: `bushfire`
* Media Cloud collections:
  * `Australia - National` https://sources.mediacloud.org/#/collections/34412282
  * `Australia - State & Local` https://sources.mediacloud.org/#/collections/38378024
* From: `r min(raw_bush.df$posix)`
* To: `r max(raw_bush.df$posix)`

## Sources

```{r}
raw_bush.df %>%
  dplyr::group_by(media_name) %>%
  dplyr::summarize(n = n(),
                   `%` = round(n() / nrow(raw_bush.df) * 100,2)) %>%
  dplyr::arrange(desc(n)) %>%
  dplyr::mutate(media_name = gsub("\\|", "~", media_name)) %>%
kable(format = 'markdown')
```


```{r}
bush_count.df <-
  raw_bush.df %>%
  dplyr::group_by(day = as.Date(posix)) %>%
  dplyr::count()
peak_day <- 
  bush_count.df$day[which.max(bush_count.df$n)]
```

* Peak day: `r peak_day`

```{r, fig.cap="Frequency distribution and 60-day window around peak"}
bush_count.df %>%
ggplot(aes(x=day,y=n)) +
  geom_line() +
  geom_vline(xintercept = c(peak_day-30, peak_day+30))
```

# Coronavirus

```{r}
raw_corona.df <- 
  read.csv("coronavirus-all-story-urls-20200504062305.csv",
           stringsAsFactors = F)
raw_corona.df$posix <- 
  as.POSIXct(raw_corona.df$publish_date, tz = "CET")
```

* Records: `r nrow(raw_corona.df)`
* Search term: `coronavirus`
* Media Cloud collections:
  * `Australia - National` https://sources.mediacloud.org/#/collections/34412282
  * `Australia - State & Local` https://sources.mediacloud.org/#/collections/38378024
* From: `r min(raw_corona.df$posix)`
* To: `r max(raw_corona.df$posix)`

## Sources

```{r}
raw_corona.df %>%
  dplyr::group_by(media_name) %>%
  dplyr::summarize(n = n(),
                   `%` = round(n() / nrow(raw_corona.df) * 100,2)) %>%
  dplyr::arrange(desc(n)) %>%
  dplyr::mutate(media_name = gsub("\\|", "~", media_name)) %>%
kable(format = 'markdown')
```


```{r}
corona_count.df <-
  raw_corona.df %>%
  dplyr::group_by(day = as.Date(posix)) %>%
  dplyr::count()
peak_day <- 
  corona_count.df$day[which.max(corona_count.df$n)]
```

* Peak day: `r peak_day`

```{r, fig.cap="Frequency distribution and 60-day window around peak"}
corona_count.df %>%
ggplot(aes(x=day,y=n)) +
  geom_line() +
  geom_vline(xintercept = c(peak_day-30, peak_day+30))
```
